### 2020-08-26 benchmarking/benchmarkingVM/ESS_round1_real.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:24
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries Comparison of cons (\textit{real}) and nocons (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [nocons (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [cons (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,365.38) --
	(212.78,578.16) --
	(281.53,578.16) --
	(281.53,494.30) --
	(  0.00,212.78) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,339.95) --
	(238.21,578.16) --
	(281.53,578.16) --
	(281.53,519.74) --
	(  0.00,238.21) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,314.51) --
	(263.65,578.16) --
	(281.53,578.16) --
	(281.53,545.17) --
	(  0.00,263.65) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.64,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.62) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (108.20,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,401.18) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 81.11,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,375.75) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.14,457.67) --
	(163.00,457.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.72,454.14) --
	(158.72,460.63);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.72,454.44) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.97,498.27) --
	(218.78,498.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.83,495.92) --
	(212.83,500.36);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.83,494.24) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.45,498.59) --
	(180.15,498.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.32,497.51) --
	(179.32,499.62);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.32,494.56) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.49,453.46) --
	(152.86,453.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.95,449.76) --
	(149.95,456.55);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.95,449.43) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.64,437.17) --
	(165.01,437.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.30,434.91) --
	(161.30,439.18);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.30,434.26) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.32,508.76) --
	(221.15,508.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.74,507.98) --
	(220.74,509.51);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.74,505.85) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.30,494.32) --
	(194.81,494.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,491.54) --
	(193.60,496.74);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,491.10) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.85,498.07) --
	(214.19,498.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,494.17) --
	(210.49,501.29);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,494.04) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.48,503.25) --
	(210.75,503.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.13,501.60) --
	(210.13,504.76);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.13,499.21) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.18,482.71) --
	(198.08,482.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,479.66) --
	(195.79,485.33);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.79,478.68) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.48,485.22) --
	(198.60,485.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.57,481.89) --
	(197.57,488.04);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.57,482.32) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.10,512.25) --
	(223.18,512.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.65,510.74) --
	(222.65,513.65);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.65,509.35) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.17,469.31) --
	(197.17,474.08);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.17,468.62) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.45,504.24) --
	(220.93,504.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.97,503.56) --
	(217.97,504.90);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.97,500.21) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.42,505.36) --
	(222.61,505.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.85,505.09) --
	(216.85,505.62);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.85,501.33) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.48,442.96) --
	(169.48,453.47);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.48,444.93) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.56,462.82) --
	(196.56,467.56);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.56,462.44) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.70,512.26) --
	(223.15,512.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.93,512.04) --
	(222.93,512.48);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.93,509.36) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.68,478.88) --
	(192.68,485.07);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.68,479.01) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.72,496.18) --
	(218.04,496.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.74,494.03) --
	(205.74,498.10);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.74,492.14) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.70,503.25) --
	(229.53,503.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.55,502.95) --
	(224.55,503.55);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.55,499.22) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.85,475.04) --
	(211.32,475.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.84,472.97) --
	(200.84,476.90);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.84,471.00) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.62,480.49) --
	(206.62,483.96);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.62,479.40) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.33,511.89) --
	(223.37,511.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.86,511.27) --
	(222.86,512.49);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.86,508.99) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.91,482.52) --
	(221.91,491.18);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.91,484.13) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.65,482.61) --
	(202.65,488.22);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.65,481.59) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.21,500.97) --
	(230.61,500.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,500.31) --
	(220.94,501.61);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.94,496.94) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.32,486.64) --
	(193.67,486.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.26,482.99) --
	(185.26,489.69);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.26,482.61) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.68,479.70) --
	(207.68,488.91);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.68,481.98) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.95,439.54) --
	(137.90,439.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.04,432.27) --
	(131.04,444.73);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.04,436.31) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.56,498.07) --
	(210.93,498.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.02,496.36) --
	(208.02,499.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.02,494.03) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.81,497.45) --
	(135.01,497.45);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:32:33
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries cons (\textit{real}) vs. nocons (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00,368.65) --
	(209.51,578.16);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (283.33,578.16) --
	(283.33,492.84) --
	(  0.00,209.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,342.13) --
	(236.03,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
	(283.33,519.37) --
	(  0.00,236.03);

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00,315.60) --
	(262.56,578.16);

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (283.33,578.16) --
	(283.33,545.89) --
	(  0.00,262.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,429.88) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,403.36) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.87,491.63) --
	(153.32,491.63);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.28,489.68) --
	(143.28,493.39);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.28,488.40) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.77,470.99) --
	(175.39,470.99);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.58,468.16) --
	(166.58,473.45);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.58,466.95) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.16,500.74) --
	(215.69,500.74);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.51,500.34) --
	(211.51,501.13);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.51,496.70) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.45,479.76) --
	(197.91,479.76);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.80,477.75) --
	(189.80,481.58);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.80,475.72) {$h$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.12,482.07) --
	(177.22,482.07);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.87,479.79) --
	(165.87,484.11);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.87,479.17) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (222.16,504.36) --
	(223.91,504.36);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.06,503.90) --
	(223.06,504.81);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.06,501.45) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.77,450.33) --
	(180.77,456.96);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.77,450.70) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.28,471.34) --
	(186.05,471.34);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.66,470.84) --
	(173.66,471.83);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.66,467.31) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.13,489.98) --
	(211.57,489.98);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.21,489.60) --
	(204.21,490.35);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.21,485.95) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.71,426.99) --
	(158.71,436.27);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,428.15) {$h$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.28,442.01) --
	(181.28,450.04);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.28,443.54) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.92,494.39) --
	(211.41,494.39);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.17,494.00) --
	(211.17,494.78);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.17,491.49) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.69,458.54) --
	(151.89,458.54);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.84,457.29) --
	(140.84,459.71);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.84,455.31) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.21,465.08) --
	(177.74,465.08);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.44,464.31) --
	(166.44,465.81);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.44,461.04) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.37,486.12) --
	(198.07,486.12);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.42,485.75) --
	(192.42,486.49);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.42,482.09) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.08,451.24) --
	(158.21,451.24);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.10,449.98) --
	(149.10,452.42);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.10,447.21) {$h$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.18,448.42) --
	(157.07,448.42);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.16,445.27) --
	(146.16,451.13);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.16,445.52) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.39,493.75) --
	(211.29,493.75);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.85,493.47) --
	(210.85,494.02);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.85,490.85) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.38,424.42) --
	(130.68,424.42);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.38,421.26) --
	(127.38,427.12);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.38,421.19) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.20,468.06) --
	(169.06,468.06);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.86,465.26) --
	(160.86,470.50);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.86,464.02) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.44,466.43) --
	(152.81,466.43);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.13,465.29) --
	(152.13,467.52);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.13,462.40) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.33,419.53) --
	(117.33,419.53);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.75,415.02) --
	(113.75,423.18);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (113.75,415.50) {$h$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.65,403.30) --
	(135.78,403.30);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.66,401.93) --
	(130.66,404.58);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.66,400.39) {$\sigma$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.69,475.61) --
	(192.26,475.61);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.98,474.76) --
	(191.98,476.41);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.98,472.70) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,466.92) --
	(187.12,473.64);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.12,467.35) {$p$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.14,476.78) --
	(180.14,480.98);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.14,474.96) {$L$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.84,493.07) --
	(230.43,493.07);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.81,492.69) --
	(224.81,493.45);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.81,489.04) {$r$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.46,463.13) --
	(211.65,463.13);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.82,460.82) --
	(200.82,465.20);
\definecolor{drawColor}{RGB}{0,216,255}
